LCS Tool: A Computational Platform for Lagrangian Coherent Structures

### 2014-11-28 main.tex
Update FIXME comments
Update Bickley jet and ocean data figures

% FIXME Performance also described in Conclusions section
The scripts call LCS Tool functions.
These functions are written to achieve balance between ease of use and performance.
% FIXME List demo script run-times in minutes in a table
Running the demo scripts takes on the order of minutes.

@@

\begin{figure}
\centering
% FIXME Shrink line LCS figure does not treat periodic boundary condition correctly
\includegraphics[width=.475\textwidth]{graphics/bickley_jet/lambda_hyperbolic_lcs}
\caption{
LCSs in the Bickley jet.
Resolution is $500 \times 200$.
Elliptic LCSs are green, shrink line LCSs are red and stretch line LCSs are blue.
White dots indicate $\lambda_2$ maxima for shrink lines and $\lambda_1$ minima stretch lines.
FTLE shown in the background.
$\lambda$ values of elliptic LCSs from left to right are [0.95,\,0.80,\,0.94,\,0.80,\,0.94], $\lambda \in [0.80,1.20]$, $\Delta\lambda = 0.01$.
}
\label{f:Bickley jet LCS}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=.475\textwidth]{graphics/ocean_dataset/lambda_hyperbolic_lcs}
\end{center}
\caption{
LCSs in the ocean velocity data from satellite altimetry.
Resolution is $400 \times 400$.
Elliptic LCSs are green, shrink line LCSs are red and stretch line LCSs are blue.
White dots indicate $\lambda_2$ maxima for shrink lines and $\lambda_1$ minima stretch lines.
FTLE shown in the background.
$\lambda = 1.00, 1.08, 0.94, 0.90, 1.06$.
}
\label{f:ocean dataset LCS}
\end{figure}

>>>>

% FIXME Performance also described in Conclusions section
The scripts call LCS Tool functions.
These functions are written to achieve balance between ease of use and performance.
% FIXME With lambda range running demos can take over an hour.
% FIXME List runtime of demo scripts in a table
Running the demo scripts takes on the order of minutes.

@@

\begin{figure}
\centering
\setlength\figurewidth{.35\textwidth}
\import{graphics/bickley_jet/}{elliptic_repelling_lcs_details.tikz}
\import{graphics/bickley_jet/}{elliptic_attracting_lcs_details.tikz}
\caption{
LCSs in the Bickley jet.
Resolution is $500 \times 200$.
Elliptic LCSs are green, shrink line LCSs are red and stretch line LCSs are blue.
White dots indicate $\lambda_2$ maxima for shrink lines and $\lambda_1$ minima stretch lines.
FTLE shown in the background.
$\lambda$ values of elliptic LCSs from left to right are [0.95,\,0.80,\,0.94,\,0.80,\,0.94], $\lambda \in [0.80,1.20]$, $\Delta\lambda = 0.01$.
}
\label{f:Bickley jet LCS}
\end{figure}

@@

\begin{figure}
\begin{center}
\setlength\figurewidth{.4\textwidth}
\import{graphics/ocean_dataset/}{elliptic_repelling_lcs.tikz}
\import{graphics/ocean_dataset/}{elliptic_attracting_lcs.tikz}
\end{center}
\caption{
LCSs in the ocean velocity data from satellite altimetry.
Resolution is $400 \times 400$.
Elliptic LCSs are green, shrink line LCSs are red and stretch line LCSs are blue.
White dots indicate $\lambda_2$ maxima for shrink lines and $\lambda_1$ minima stretch lines.
FTLE shown in the background.
$\lambda = 1.00, 1.08, 0.94, 0.90, 1.06$.
}
\label{f:ocean dataset LCS}
\end{figure}
